Demographic Species Distribution Models

### 2019-10-03 manuscript/ms.Rmd
code tweaks and compare DSDM with GLM for BBS data
rescale against MAPS survey locations yielding vital rate estimates

\begin{align}
ln(F_i) &= ln(\widetilde{F}) + \mathbf{X}_{Fi}\beta_F \\ \nonumber
logit(S_{Ai}) &= logit(\widetilde{S}_A) + \mathbf{X}_{Si}\beta_S \\ \nonumber
logit(S_{Ji}) &= logit(S_{Ai}) - 0.94 \\ \nonumber
\widetilde{F} &\sim N^+(-0.545, 0.25^2) \\ \nonumber
\widetilde{S}_A &\sim N^{(0,1)}(0.895, 0.195^2) \\ \nonumber
\beta_{Si} &\sim N(0, 10) \\ \nonumber
\beta_{Fi} &\sim N(0, 10)
\end{align}

>>>>

\begin{align}
ln(F_i) &= ln(\widetilde{F}) + \mathbf{X}_{Fi}\beta_F \\ \nonumber
logit(S_{Ai}) &= logit(\widetilde{S}_A) + \mathbf{X}_{Si}\beta_S \\ \nonumber
logit(S_{Ji}) &= logit(S_{Ai}) - 0.94 \\ \nonumber
\widetilde{F} &\sim N^+(-0.545, 0.25^2) \\ \nonumber
\widetilde{S}_A &\sim N^{(0,1)}(0.895, 0.195^2) \\ \nonumber
\beta_{Si} &\sim N(0, 1) \\ \nonumber
\beta_{Fi} &\sim N(0, 1)
\end{align}

TODO:
 - change this to have generic intercepts ($\alpha_F$ and $\alpha_S$), then define those intercepts below.
 - reword the below dso that the general formulation doesn't talk about the priors for the intercepts
 - introduce all the parts of the model here first, then have a section below this where we talk about prior ($\alpha_F \sim N(0.58, 0.25 ^ 2)$ etc.)
 - reword the centring of X to make it clear we are centreing against the (weighted) locations where the fecundity and survival estimates were made.
